---
title: "Modelling"
author: "Samuel Chan"
date: 29/10/2023
date-format: "DD/MM/YYYY"
format: html
editor: visual
---

# Load libraries

```{r}
library(tidyverse)
library(rstan)
library(brms)
library(performance)
library(DHARMa)
library(HDInterval)
library(emmeans)
library(tidybayes)
library(patchwork)
library(ggpubr)
library(visibly)
set.seed(13)
```

## Read data and preparation

Data have been edited to include 0s which were not allowed for TD/PD/FD calculations

```{r}
results.sp.Div <- read.csv("../outputs/results.sp.Div2_edit.csv", header = T)

results.ge.Div <- read.csv("../outputs/results.ge.Div2_edit.csv", header = T)

meta.sp  <- results.sp.Div %>%
  select(., Site, Location, Year:Replicate)

meta.ge <- results.ge.Div %>%
  select(., Site, Location, Year:Depth, Replicate)

res.sp <- results.sp.Div %>%
  ungroup() %>%
  select(., Abun:RaoQ) %>%
  select(., -nbsp, -sing.sp, -qual.FRic, - FEve, -FDiv, -FDis) %>%
  dplyr::rename(., FDiv = RaoQ) 

res.sp.scaled <- scale(res.sp, scale = T, center = T)

res.sp.cwm <- results.sp.Div %>% 
  select(., starts_with("CWM")) %>%
  select(., CWM.grow:CWM.cmd, CWM.branching:CWM.submassive)

res.sp.cwm.modes <-results.sp.Div %>%
  select(., CWM.col:CWM.symb)

res.sp.cwm.scaled <- scale(res.sp.cwm, scale = T, center = T)

res.ge <- results.ge.Div %>%
  ungroup() %>%
  select(., Abun:RaoQ) %>%
  select(., -nbsp, -sing.sp, -qual.FRic, - FEve, -FDiv, -FDis) %>%
  dplyr::rename(., FDiv = RaoQ) 

res.ge.scaled <- scale(res.ge, scale = T, center = T)

res.ge.cwm <- results.ge.Div %>%
  select(., starts_with("CWM")) %>%
  select(., CWM.grow:CWM.cmd, CWM.branching:CWM.submassive)

res.ge.cwm.modes <-results.ge.Div %>%
  select(., CWM.col:CWM.symb)

res.ge.cwm.scaled <- scale(res.ge.cwm, scale = T, center = T)
```

## Modelling datasets

```{r}
res.sp.div.sc <- cbind(meta.sp, res.sp.scaled)
res.ge.div.sc <- cbind(meta.ge, res.ge.scaled)

res.sp.div <- cbind(meta.sp, res.sp)
res.ge.div <- cbind(meta.ge, res.ge)

res.sp.cwm.sc <- cbind(meta.sp, res.sp.cwm.scaled)
res.ge.cwm.sc <- cbind(meta.ge, res.ge.cwm.scaled)

res.sp.cwm.us <- cbind(meta.sp, res.sp.cwm)
res.ge.cwm.us <- cbind(meta.ge, res.ge.cwm)

res.sp.cwm.mo <- cbind(meta.sp, res.sp.cwm.modes)
res.ge.cwm.mo <- cbind(meta.ge, res.ge.cwm.modes)

rm(meta.sp);rm(meta.ge)
#rm(res.sp.scaled);rm(res.ge.scaled)
rm(res.sp);rm(res.ge)
rm(results.sp.Div);rm(results.ge.Div)

rm(res.sp.cwm.modes);rm(res.ge.cwm.modes)
rm(res.sp.cwm.scaled);rm(res.ge.cwm.scaled)
rm(res.sp.cwm);rm(res.ge.cwm)
```

# Assess model fits for random effect structures

```{r}
model.sp.abun <- brm(Abun ~ s(Year) + Site, data=res.sp.div, cores = 2)
model.sp.tric <- brm(TRic ~ s(Year) + Site, data=res.sp.div, cores = 2)
model.sp.tdiv <- brm(TDiv ~ s(Year) + Site, data=res.sp.div, cores = 2)
model.sp.pric <- brm(PRic ~ s(Year) + Site, data=res.sp.div, cores = 2)
model.sp.pdiv <- brm(PDiv ~ s(Year) + Site, data=res.sp.div, cores = 2)
model.sp.fric <- brm(FRic ~ s(Year) + Site, data=res.sp.div, cores = 2)
model.sp.fdiv <- brm(FDiv ~ s(Year) + Site, data=res.sp.div, cores = 2)

model.sp.abun.re <- brm(Abun ~ s(Year) + (1|Site), data=res.sp.div, cores = 2)
model.sp.tric.re <- brm(TRic ~ s(Year) + (1|Site), data=res.sp.div, cores = 2)
model.sp.tdiv.re <- brm(TDiv ~ s(Year) + (1|Site), data=res.sp.div, cores = 2)
model.sp.pric.re <- brm(PRic ~ s(Year) + (1|Site), data=res.sp.div, cores = 2)
model.sp.pdiv.re <- brm(PDiv ~ s(Year) + (1|Site), data=res.sp.div, cores = 2)
model.sp.fric.re <- brm(FRic ~ s(Year) + (1|Site), data=res.sp.div, cores = 2)
model.sp.fdiv.re <- brm(FDiv ~ s(Year) + (1|Site), data=res.sp.div, cores = 2)

model.sp.abun.re2 <- brm(Abun ~ s(Year) + (1|Location), data=res.sp.div, cores = 2)
model.sp.tric.re2 <- brm(TRic ~ s(Year) + (1|Location), data=res.sp.div, cores = 2)
model.sp.tdiv.re2 <- brm(TDiv ~ s(Year) + (1|Location), data=res.sp.div, cores = 2)
model.sp.pric.re2 <- brm(PRic ~ s(Year) + (1|Location), data=res.sp.div, cores = 2)
model.sp.pdiv.re2 <- brm(PDiv ~ s(Year) + (1|Location), data=res.sp.div, cores = 2)
model.sp.fric.re2 <- brm(FRic ~ s(Year) + (1|Location), data=res.sp.div, cores = 2)
model.sp.fdiv.re2 <- brm(FDiv ~ s(Year) + (1|Location), data=res.sp.div, cores = 2)

model.sp.abun.ren <- brm(Abun ~ s(Year) + (1|Location/Site), data=res.sp.div, cores = 2)
model.sp.tric.ren <- brm(TRic ~ s(Year) + (1|Location/Site), data=res.sp.div, cores = 2)
model.sp.tdiv.ren <- brm(TDiv ~ s(Year) + (1|Location/Site), data=res.sp.div, cores = 2)
model.sp.pric.ren <- brm(PRic ~ s(Year) + (1|Location/Site), data=res.sp.div, cores = 2)
model.sp.pdiv.ren <- brm(PDiv ~ s(Year) + (1|Location/Site), data=res.sp.div, cores = 2)
model.sp.fric.ren <- brm(FRic ~ s(Year) + (1|Location/Site), data=res.sp.div, cores = 2)
model.sp.fdiv.ren <- brm(FDiv ~ s(Year) + (1|Location/Site), data=res.sp.div, cores = 2)
```

## LOO comparisons

```{r}
loo(model.sp.abun, model.sp.abun.re, model.sp.abun.re2, model.sp.abun.ren)
loo(model.sp.tric, model.sp.tric.re, model.sp.tric.re2, model.sp.tric.ren)
loo(model.sp.tdiv, model.sp.tdiv.re, model.sp.tdiv.re2, model.sp.tdiv.ren)
loo(model.sp.pric, model.sp.pric.re, model.sp.pric.re2, model.sp.pric.ren)
loo(model.sp.pdiv, model.sp.pdiv.re, model.sp.pdiv.re2, model.sp.pdiv.ren)
loo(model.sp.fric, model.sp.fric.re, model.sp.fric.re2, model.sp.fric.ren)
loo(model.sp.fdiv, model.sp.fdiv.re, model.sp.fdiv.re2, model.sp.fdiv.ren)

rm(model.sp.abun);rm(model.sp.abun.re);rm(model.sp.abun.re2);rm(model.sp.abun.ren)
rm(model.sp.tric);rm(model.sp.tric.re);rm(model.sp.tric.re2);rm(model.sp.tric.ren)
rm(model.sp.tdiv);rm(model.sp.tdiv.re);rm(model.sp.tdiv.re2);rm(model.sp.tdiv.ren)
rm(model.sp.pric);rm(model.sp.pric.re);rm(model.sp.pric.re2);rm(model.sp.pric.ren)
rm(model.sp.abun);rm(model.sp.abun.re);rm(model.sp.abun.re2);rm(model.sp.abun.ren)
rm(model.sp.abun);rm(model.sp.abun.re);rm(model.sp.abun.re2);rm(model.sp.abun.ren)
rm(model.sp.abun);rm(model.sp.abun.re);rm(model.sp.abun.re2);rm(model.sp.abun.ren)
```

LOO indicates little difference between Site as random effect vs nested Location/Site so we default to the simpler model

# Setting priors

```{r}
get_prior(Abun ~ s(Year) + (1|Site), data = res.sp.div)

scaled.priors <- prior(normal(0, 1), class = "Intercept") + 
  prior(normal(0, 2), class = "b") +
  prior(student_t(3, 0, 2), class = "sd") +
  prior(normal(0, 2), class = "sds")

scaled.priors.cor <- prior(normal(0, 1), class = "Intercept") + 
  prior(normal(0, 2), class = "b") +
  prior(normal(0, 2), class = "sds")
```

# Diversity models

## Species diversity models

### Abundance

```{r}
model.sp.abun.re.sc <- brm(Abun ~ s(Year) + (1|Site), 
                           data=res.sp.div.sc, 
                           prior = scaled.priors,
                           cores = 4, 
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
```

### Taxonomic richness and diversity

```{r}
model.sp.tric.re.sc <- brm(TRic ~ s(Year) + (1|Site), 
                           data=res.sp.div.sc, 
                           prior = scaled.priors,
                           cores = 4, 
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
model.sp.tdiv.re.sc <- brm(TDiv ~ s(Year) + (1|Site), data=res.sp.div.sc, 
                           prior = scaled.priors,
                           cores = 4, 
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
```

### Phylogenetic richness and diversity

```{r}
model.sp.pric.re.sc <- brm(PRic ~ s(Year) + (1|Site), data=res.sp.div.sc, 
                           prior = scaled.priors,
                           cores = 4, 
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
model.sp.pdiv.re.sc <- brm(PDiv ~ s(Year) + (1|Site), data=res.sp.div.sc, 
                           prior = scaled.priors,
                           cores = 4, 
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
```

### Functional richness and diversity

```{r}
model.sp.fric.re.sc <- brm(FRic ~ s(Year) + (1|Site), data=res.sp.div.sc, 
                           prior = scaled.priors,
                           cores = 4, 
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
model.sp.fdiv.re.sc <- brm(FDiv ~ s(Year) + (1|Site), data=res.sp.div.sc, 
                           prior = scaled.priors,
                           cores = 4, 
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
```

## Genus diversity models

### Abundance

```{r}
model.ge.abun.re.sc <- brm(Abun ~ s(Year) + (1|Site), data=res.ge.div.sc, 
                           prior = scaled.priors,
                           cores = 4, 
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
```

### Taxonomic richness and diversity

```{r}
model.ge.tric.re.sc <- brm(TRic ~ s(Year) + (1|Site), data=res.ge.div.sc, 
                           prior = scaled.priors,
                           cores = 4, 
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
model.ge.tdiv.re.sc <- brm(TDiv ~ s(Year) + (1|Site), data=res.ge.div.sc, 
                           prior = scaled.priors,
                           cores = 4, 
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
```

### Phylogenetic richness and diversity

```{r}
model.ge.pric.re.sc <- brm(PRic ~ s(Year) + (1|Site), data=res.ge.div.sc, 
                           prior = scaled.priors,
                           cores = 4, 
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
model.ge.pdiv.re.sc <- brm(PDiv ~ s(Year) + (1|Site), data=res.ge.div.sc, 
                           prior = scaled.priors,
                           cores = 4, 
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
```

### Functional richness and diversity

```{r}
model.ge.fric.re.sc <- brm(FRic ~ s(Year) + (1|Site), data=res.ge.div.sc, 
                           prior = scaled.priors,
                           cores = 4, 
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
model.ge.fdiv.re.sc <- brm(FDiv ~ s(Year) + (1|Site), data=res.ge.div.sc, 
                           prior = scaled.priors,
                           cores = 4, 
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
```

# CWM models

## Species CWM models

### Continuous traits

```{r}
model.sp.grow.re.sc <- brm(CWM.grow ~ s(Year) + (1|Site), 
                           data=res.sp.cwm.sc, 
                           prior = scaled.priors,
                           cores = 4,
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
model.sp.skel.re.sc <- brm(CWM.skel ~ s(Year) + (1|Site), 
                           data=res.sp.cwm.sc, 
                           prior = scaled.priors,
                           cores = 4,
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
model.sp.cwid.re.sc <- brm(CWM.corwidth ~ s(Year) + (1|Site), 
                           data=res.sp.cwm.sc, 
                           prior = scaled.priors,
                           cores = 4,
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
model.sp.cmd.re.sc <- brm(CWM.cmd ~ s(Year) + (1|Site), 
                           data=res.sp.cwm.sc, 
                           prior = scaled.priors,
                           cores = 4,
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
```

### Growth forms

```{r}
model.sp.gfbr.re.sc <- brm(CWM.branching ~ s(Year) + (1|Site), 
                           data=res.sp.cwm.sc, 
                           prior = scaled.priors,
                           cores = 4,
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
model.sp.gfen.re.sc <- brm(CWM.encrusting ~ s(Year) + (1|Site), 
                           data=res.sp.cwm.sc, 
                           prior = scaled.priors,
                           cores = 4,
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
model.sp.gfla.re.sc <- brm(CWM.laminar ~ s(Year) + (1|Site), 
                           data=res.sp.cwm.sc, 
                           prior = scaled.priors,
                           cores = 4,
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
model.sp.gfma.re.sc <- brm(CWM.massive ~ s(Year) + (1|Site), 
                          data=res.sp.cwm.sc, 
                          prior = scaled.priors,
                          cores = 4,
                          iter = 5000,
                          warmup = 1000,
                          thin = 5)
model.sp.gfsu.re.sc <- brm(CWM.submassive ~ s(Year) + (1|Site), 
                           data=res.sp.cwm.sc, 
                           prior = scaled.priors,
                           cores = 4,
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
```

## Genus CWM models

### Continuous traits

```{r}
model.ge.grow.re.sc <- brm(CWM.grow ~ s(Year) + (1|Site), 
                           data=res.ge.cwm.sc, 
                           prior = scaled.priors,
                           cores = 4,
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
model.ge.skel.re.sc <- brm(CWM.skel ~ s(Year) + (1|Site), 
                           data=res.ge.cwm.sc, 
                           prior = scaled.priors,
                           cores = 4,
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
model.ge.cwid.re.sc <- brm(CWM.corwidth ~ s(Year) + (1|Site), 
                           data=res.ge.cwm.sc, 
                           prior = scaled.priors,
                           cores = 4,
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
model.ge.cmd.re.sc <- brm(CWM.cmd ~ s(Year) + (1|Site), 
                          data=res.ge.cwm.sc, 
                          prior = scaled.priors,
                          cores = 4,
                          iter = 5000,
                          warmup = 1000,
                          thin = 5)
```

### Growth forms

```{r}
model.ge.gfbr.re.sc <- brm(CWM.branching ~ s(Year) + (1|Site), 
                           data=res.ge.cwm.sc, 
                           prior = scaled.priors,
                           cores = 4,
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
model.ge.gfen.re.sc <- brm(CWM.encrusting ~ s(Year) + (1|Site), 
                           data=res.ge.cwm.sc, 
                           prior = scaled.priors,
                           cores = 4,
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
model.ge.gfla.re.sc <- brm(CWM.laminar ~ s(Year) + (1|Site), 
                           data=res.ge.cwm.sc, 
                           prior = scaled.priors,
                           cores = 4,
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
model.ge.gfma.re.sc <- brm(CWM.massive ~ s(Year) + (1|Site), 
                           data=res.ge.cwm.sc, 
                           prior = scaled.priors,
                           cores = 4,
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
model.ge.gfsu.re.sc <- brm(CWM.submassive ~ s(Year) + (1|Site), 
                           data=res.ge.cwm.sc, 
                           prior = scaled.priors,
                           cores = 4,
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
```

# Assessing model fits for correlation models

## Species richness correlations

```{r}
scor.pric.sc <- brm(PRic ~ s(TRic), data=res.sp.div.sc,
                    prior = scaled.priors.cor,
                    cores = 4,
                    iter = 5000,
                    warmup = 1000,
                    thin = 5)
scor.fric.sc <- brm(FRic ~ s(TRic), data=res.sp.div.sc,
                    prior = scaled.priors.cor,
                    cores = 4,
                    iter = 5000,
                    warmup = 1000,
                    thin = 5)
scor.pfric.sc <- brm(FRic ~ s(PRic), data=res.sp.div.sc,
                     prior = scaled.priors.cor,
                     cores = 4,
                     iter = 5000,
                     warmup = 1000,
                     thin = 5)

scor.pric.sc2 <- brm(PRic ~ s(TRic) + (1|Site), data=res.sp.div.sc,
                    prior = scaled.priors,
                    cores = 4,
                    iter = 5000,
                    warmup = 1000,
                    thin = 5)
scor.fric.sc2 <- brm(FRic ~ s(TRic) + (1|Site), data=res.sp.div.sc,
                    prior = scaled.priors,
                    cores = 4,
                    iter = 5000,
                    warmup = 1000,
                    thin = 5)
scor.pfric.sc2 <- brm(FRic ~ s(PRic) + (1|Site), data=res.sp.div.sc,
                     prior = scaled.priors,
                     cores = 4,
                     iter = 5000,
                     warmup = 1000,
                     thin = 5)
```

## Species diversity correlations

```{r}
scor.pdiv.sc <- brm(PDiv ~ s(TDiv), data=res.sp.div.sc,
                 prior = scaled.priors.cor,
                 cores = 4,
                 iter = 5000,
                 warmup = 1000,
                 thin = 5)
scor.fdiv.sc <- brm(FDiv ~ s(TDiv), data=res.sp.div.sc,
                 prior = scaled.priors.cor,
                 cores = 4,
                 iter = 5000,
                 warmup = 1000,
                 thin = 5)
scor.pfdiv.sc <- brm(FDiv ~ s(PDiv), data=res.sp.div.sc,
                  prior = scaled.priors.cor,
                  cores = 4,
                  iter = 5000,
                  warmup = 1000,
                  thin = 5)

scor.pdiv.sc2 <- brm(PDiv ~ s(TDiv) + (1|Site), data=res.sp.div.sc,
                    prior = scaled.priors,
                    cores = 4,
                    iter = 5000,
                    warmup = 1000,
                    thin = 5)
scor.fdiv.sc2 <- brm(FDiv ~ s(TDiv) + (1|Site), data=res.sp.div.sc,
                    prior = scaled.priors,
                    cores = 4,
                    iter = 5000,
                    warmup = 1000,
                    thin = 5)
scor.pfdiv.sc2 <- brm(FDiv ~ s(PDiv) + (1|Site), data=res.sp.div.sc,
                    prior = scaled.priors.cor,
                    cores = 4,
                    iter = 5000,
                    warmup = 1000,
                    thin = 5)
```

## Genus richness correlations

```{r}
cor.pric.sc <- brm(PRic ~ s(TRic), data=res.ge.div.sc,
                   prior = scaled.priors.cor,
                   cores = 4,
                   iter = 5000,
                   warmup = 1000,
                   thin = 5)
cor.fric.sc <- brm(FRic ~ s(TRic), data=res.ge.div.sc,
                   prior = scaled.priors.cor,
                   cores = 4,
                   iter = 5000,
                   warmup = 1000,
                   thin = 5)
cor.pfric.sc <- brm(FRic ~ s(PRic), data=res.ge.div.sc,
                    prior = scaled.priors.cor,
                    cores = 4,
                    iter = 5000,
                    warmup = 1000,
                    thin = 5)

cor.pric.sc2 <- brm(PRic ~ s(TRic) + (1|Site), data=res.ge.div.sc,
                   prior = scaled.priors,
                   cores = 4,
                   iter = 5000,
                   warmup = 1000,
                   thin = 5)
cor.fric.sc2 <- brm(FRic ~ s(TRic) + (1|Site), data=res.ge.div.sc,
                   prior = scaled.priors,
                   cores = 4,
                   iter = 5000,
                   warmup = 1000,
                   thin = 5)
cor.pfric.sc2 <- brm(FRic ~ s(PRic) + (1|Site), data=res.ge.div.sc,
                    prior = scaled.priors,
                    cores = 4,
                    iter = 5000,
                    warmup = 1000,
                    thin = 5)

cor.pdiv.sc2 <- brm(PDiv ~ s(TDiv) + (1|Site), data=res.ge.div.sc,
                   prior = scaled.priors,
                   cores = 4,
                   iter = 5000,
                   warmup = 1000,
                   thin = 5)
cor.fdiv.sc2 <- brm(FDiv ~ s(TDiv) + (1|Site), data=res.ge.div.sc,
                   prior = scaled.priors,
                   cores = 4,
                   iter = 5000,
                   warmup = 1000,
                   thin = 5)
cor.pfdiv.sc2 <- brm(FDiv ~ s(PDiv) + (1|Site), data=res.ge.div.sc,
                    prior = scaled.priors,
                    cores = 4,
                    iter = 5000,
                    warmup = 1000,
                    thin = 5)
```

## Genus diversity correlations

```{r}
cor.pdiv.sc <- brm(PDiv ~ s(TDiv), data=res.ge.div.sc,
                prior = scaled.priors.cor,
                cores = 4,
                iter = 5000,
                warmup = 1000,
                thin = 5)
cor.fdiv.sc <- brm(FDiv ~ s(TDiv), data=res.ge.div.sc,
                prior = scaled.priors.cor,
                cores = 4,
                iter = 5000,
                warmup = 1000,
                thin = 5)
cor.pfdiv.sc <- brm(FDiv ~ s(PDiv), data=res.ge.div.sc,
                 prior = scaled.priors.cor,
                 cores = 4,
                 iter = 5000,
                 warmup = 1000,
                 thin = 5)
```

## LOO comparisons

```{r}
loo(cor.fdiv.sc,cor.fdiv.sc2)
loo(cor.pdiv.sc,cor.pdiv.sc2)
loo(cor.pfdiv.sc,cor.pfdiv.sc2)
loo(cor.fric.sc,cor.fric.sc2)
loo(cor.pric.sc,cor.pric.sc2)
loo(cor.pfric.sc,cor.pfric.sc2)

loo(scor.fdiv.sc,scor.fdiv.sc2)
loo(scor.pdiv.sc,scor.pdiv.sc2)
loo(scor.pfdiv.sc,scor.pfdiv.sc2)
loo(scor.fric.sc,scor.fric.sc2)
loo(scor.pric.sc,scor.pric.sc2)
loo(scor.pfric.sc,scor.pfric.sc2)
```

## Bayes R2 calculations

```{r}
bayes_R2(cor.pric.sc2)
bayes_R2(cor.fric.sc2)
bayes_R2(cor.pfric.sc2)
bayes_R2(cor.pdiv.sc2)
bayes_R2(cor.fdiv.sc2)
bayes_R2(cor.pfdiv.sc2)
bayes_R2(scor.pric.sc2)
bayes_R2(scor.fric.sc2)
bayes_R2(scor.pfric.sc2)
bayes_R2(scor.pdiv.sc2)
bayes_R2(scor.fdiv.sc2)
bayes_R2(scor.pfdiv.sc2)
```

# Diversity models for modern comparisons

## Create data

```{r}
res.sp.div.sc <- res.sp.div.sc %>%
  dplyr::filter(., Site == "CY-N" | Site == "CY-S" | Site == "HA-NE" | Site == "HA-W" | 
                  Site == "HP-W" | Site == "LZ-E" | Site == "RL-W" | Site == "SE-SW") %>%
  mutate(., Period = case_when(Year < 2000 ~ "Historical",
                               Year >= 2000 ~ "Modern"))
res.sp.cwm.sc <- res.sp.cwm.sc %>%
  dplyr::filter(., Site == "CY-N" | Site == "CY-S" | Site == "HA-NE" | Site == "HA-W" | 
                  Site == "HP-W" | Site == "LZ-E" | Site == "RL-W" | Site == "SE-SW") %>%
  mutate(., Period = case_when(Year < 2000 ~ "Historical",
                               Year >= 2000 ~ "Modern"))

scaled.priors.mod <- prior(normal(0, 1), class = "Intercept") + 
  prior(normal(0, 2), class = "b") +
  prior(student_t(3, 0, 2), class = "sd")
```

## Models

### Abundance

```{r}
model.sp.abun.re.sc <- brm(Abun ~ Period + (1|Site), 
                           data=res.sp.div.sc, 
                           prior = scaled.priors.mod,
                           cores = 4, 
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
```

### Taxonomic richness and diversity

```{r}
model.sp.tric.re.sc <- brm(TRic ~ Period + (1|Site), 
                           data=res.sp.div.sc, 
                           prior = scaled.priors.mod,
                           cores = 4, 
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
model.sp.tdiv.re.sc <- brm(TDiv ~ Period + (1|Site), data=res.sp.div.sc, 
                           prior = scaled.priors.mod,
                           cores = 4, 
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
```

### Phylogenetic richness and diversity

```{r}
model.sp.pric.re.sc <- brm(PRic ~ Period + (1|Site), 
                           data=res.sp.div.sc, 
                           prior = scaled.priors.mod,
                           cores = 4, 
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
model.sp.pdiv.re.sc <- brm(PDiv ~ Period + (1|Site), 
                           data=res.sp.div.sc, 
                           prior = scaled.priors.mod,
                           cores = 4, 
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
```

### Functional richness and diversity

```{r}
model.sp.fric.re.sc <- brm(FRic ~ Period + (1|Site), 
                           data=res.sp.div.sc, 
                           prior = scaled.priors.mod,
                           cores = 4, 
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
model.sp.fdiv.re.sc <- brm(FDiv ~ Period + (1|Site), data=res.sp.div.sc, 
                           prior = scaled.priors.mod,
                           cores = 4, 
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
```

### CWMs continuous traits

```{r}
model.sp.grow.re.sc <- brm(CWM.grow ~ Period + (1|Site), 
                           data=res.sp.cwm.sc, 
                           prior = scaled.priors.mod,
                           cores = 4,
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
model.sp.skel.re.sc <- brm(CWM.skel ~ Period + (1|Site), 
                           data=res.sp.cwm.sc, 
                           prior = scaled.priors.mod,
                           cores = 4,
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
model.sp.cwid.re.sc <- brm(CWM.corwidth ~ Period + (1|Site), 
                           data=res.sp.cwm.sc, 
                           prior = scaled.priors.mod,
                           cores = 4,
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
model.sp.cmd.re.sc <- brm(CWM.cmd ~ Period + (1|Site), 
                          data=res.sp.cwm.sc, 
                          prior = scaled.priors.mod,
                          cores = 4,
                          iter = 5000,
                          warmup = 1000,
                          thin = 5)
```

### CWMs growth forms

```{r}
model.sp.gfbr.re.sc <- brm(CWM.branching ~ Period + (1|Site), 
                           data=res.sp.cwm.sc, 
                           prior = scaled.priors.mod,
                           cores = 4,
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
model.sp.gfen.re.sc <- brm(CWM.encrusting ~ Period + (1|Site), 
                           data=res.sp.cwm.sc, 
                           prior = scaled.priors.mod,
                           cores = 4,
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
model.sp.gfla.re.sc <- brm(CWM.laminar ~ Period + (1|Site), 
                           data=res.sp.cwm.sc, 
                           prior = scaled.priors.mod,
                           cores = 4,
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
model.sp.gfma.re.sc <- brm(CWM.massive ~ Period + (1|Site), 
                           data=res.sp.cwm.sc, 
                           prior = scaled.priors.mod,
                           cores = 4,
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
model.sp.gfsu.re.sc <- brm(CWM.submassive ~ Period + (1|Site), 
                           data=res.sp.cwm.sc, 
                           prior = scaled.priors.mod,
                           cores = 4,
                           iter = 5000,
                           warmup = 1000,
                           thin = 5)
```

# Model validations

```{r}
model.ge.abun.re.sc$fit |> stan_trace()
model.ge.abun.re.sc$fit |> stan_ac()
model.ge.abun.re.sc$fit |> stan_rhat()
model.ge.abun.re.sc$fit |> stan_ess()
model.ge.abun.re.sc |>  pp_check(type = "dens_overlay", ndraws = 200)
resids <- model.ge.abun.re.sc |> make_brms_dharma_res(integerResponse = F)
testUniformity(resids)
testDispersion(resids)
plotResiduals(resids)
plotResiduals(resids, form = factor(rep(1, nrow(model.ge.abun.re.sc))))
```

# Functions from Murray Logan

```{r}
#### functions ####
make_brms_dharma_res <- function(brms_model, seed = 10, ...) {
# equivalent to `simulateResiduals(lme4_model, use.u = FALSE)`
# cores are set to 1 just to ensure reproducibility
options(mc.cores = 1)
on.exit(options(mc.cores = parallel::detectCores()))
response <- brms::standata(brms_model)$Y
ndraws <- nrow(as_draws_df(brms_model))
manual_preds_brms <- matrix(0, ndraws, nrow(brms_model$data))
random_terms <- insight::find_random(
  brms_model, split_nested = TRUE, flatten = TRUE
)
# for this to have a similar output to `glmmTMB`'s default, we need to
#   create new levels in the hierarchical variables, so then we can
#   use `allow_new_levels = TRUE` and `sample_new_levels = "gaussian"` in
#   `brms::posterior_epred`. This is equivalent to
#   `simulateResiduals(lme4_model, use.u = FALSE)`. See details in
#   `lme4:::simulate.merMod` and `glmmTMB:::simulate.glmmTMB`
new_data <- brms_model$data |>
  dplyr::mutate(across(
    all_of(random_terms), \(x)paste0("NEW_", x) |> as.factor()
  ))
set.seed(seed)
brms_sims <- brms::posterior_predict(
  brms_model, re_formula = NULL, newdata = new_data,
  allow_new_levels = TRUE, sample_new_levels = "gaussian"
) |>
  t()
fitted_median_brms <- apply(brms_sims, 1, median)
## fitted_median_brms <- apply(
##     t(brms::posterior_epred(brms_model, ndraws = ndraws, re.form = NA)),
##     1,
##     mean)
DHARMa::createDHARMa(
  simulatedResponse = brms_sims,
  observedResponse = response,
  fittedPredictedResponse = fitted_median_brms,
  ...
)
}
```
