---
title: "Outputs"
author: "Samuel Chan"
date: 29/10/2023
date-format: "DD/MM/YYYY"
format: html
editor: source
---

# Load libraries

```{r}
library(tidyverse)
library(rstan)
library(brms)
library(performance)
library(DHARMa)
library(HDInterval)
library(emmeans)
library(tidybayes)
library(patchwork)
library(ggpubr)
library(visibly)
set.seed(13)
```

# Posterior predictions

## Create dataset for predictions

```{r}
yeardata <- seq(1986, 2020, 1) %>%
  as.tibble() %>%
  rename(Year = value)
```

## Abundance

```{r}
pred.ep.abun <- posterior_epred(model.ge.abun.re.sc, newdata = yeardata, re_formula = NA) %>%
  as.tibble() %>%
  summarise_all(.funs = list(mean = mean, sd = sd)) %>%
  t() %>%
  cbind(yeardata) %>%
  mutate(Values = . * 0.1766204 + 0.2677669) %>%
  cbind(rep(c("Mean", "SD"), each = 35)) %>%
  select(., 2:4) %>%
  rename("Stat" = 3) %>%
  pivot_wider(names_from = Stat, names_prefix = c("Abun_"), values_from = Values)
```

## Taxonomic

```{r}
pred.ep.tric <- posterior_epred(model.ge.tric.re.sc, newdata = yeardata, re_formula = NA) %>%
  as.tibble() %>%
  summarise_all(.funs = list(mean = mean, sd = sd)) %>%
  t() %>%
  cbind(yeardata) %>%
  mutate(Values = . * 4.610299 + 11.0093) %>%
  cbind(rep(c("Mean", "SD"), each = 35)) %>%
  select(., 2:4) %>%
  rename("Stat" = 3) %>%
  pivot_wider(names_from = Stat, names_prefix = c("TRic_"), values_from = Values)
pred.ep.tdiv <- posterior_epred(model.ge.tdiv.re.sc, newdata = yeardata, re_formula = NA) %>%
  as.tibble() %>%
  summarise_all(.funs = list(mean = mean, sd = sd)) %>%
  t() %>%
  cbind(yeardata) %>%
  mutate(Values = . * 0.1820617 + 0.7707524) %>%
  cbind(rep(c("Mean", "SD"), each = 35)) %>%
  select(., 2:4) %>%
  rename("Stat" = 3) %>%
  pivot_wider(names_from = Stat, names_prefix = c("TDiv_"), values_from = Values)
```

## Phylogenetic

```{r}
pred.ep.pric <- posterior_epred(model.ge.pric.re.sc, newdata = yeardata, re_formula = NA) %>%
  as.tibble() %>%
  summarise_all(.funs = list(mean = mean, sd = sd)) %>%
  t() %>%
  cbind(yeardata) %>%
  mutate(Values = . * 245.0934 + 1226.477) %>%
  cbind(rep(c("Mean", "SD"), each = 35)) %>%
  select(., 2:4) %>%
  rename("Stat" = 3) %>%
  pivot_wider(names_from = Stat, names_prefix = c("PRic_"), values_from = Values)
pred.ep.pdiv <- posterior_epred(model.ge.pdiv.re.sc, newdata = yeardata, re_formula = NA) %>%
  as.tibble() %>%
  summarise_all(.funs = list(mean = mean, sd = sd)) %>%
  t() %>%
  cbind(yeardata) %>%
  mutate(Values = . * 56.61612 + 150.2985) %>%
  cbind(rep(c("Mean", "SD"), each = 35)) %>%
  select(., 2:4) %>%
  rename("Stat" = 3) %>%
  pivot_wider(names_from = Stat, names_prefix = c("PDiv_"), values_from = Values)
```

## Functional

```{r}
pred.ep.fric <- posterior_epred(model.ge.fric.re.sc, newdata = yeardata, re_formula = NA) %>%
  as.tibble() %>%
  summarise_all(.funs = list(mean = mean, sd = sd)) %>%
  t() %>%
  cbind(yeardata) %>%
  mutate(Values = . * 0.1391478 + 0.2692114) %>%
  cbind(rep(c("Mean", "SD"), each = 35)) %>%
  select(., 2:4) %>%
  rename("Stat" = 3) %>%
  pivot_wider(names_from = Stat, names_prefix = c("FRic_"), values_from = Values)
pred.ep.fdiv <- posterior_epred(model.ge.fdiv.re.sc, newdata = yeardata, re_formula = NA) %>%
  as.tibble() %>%
  summarise_all(.funs = list(mean = mean, sd = sd)) %>%
  t() %>%
  cbind(yeardata) %>%
  mutate(Values = . * 0.009244943 + 0.02164159) %>%
  cbind(rep(c("Mean", "SD"), each = 35)) %>%
  select(., 2:4) %>%
  rename("Stat" = 3) %>%
  pivot_wider(names_from = Stat, names_prefix = c("FDiv_"), values_from = Values)
```

# Posterior predictions unscaled

## Abundance

```{r}
pred.epus.abun <- posterior_epred(model.ge.abun.re.sc, newdata = yeardata, re_formula = NA) %>%
  as.tibble() %>%
  summarise_all(.funs = list(mean = mean, sd = sd)) %>%
  t() %>%
  cbind(yeardata) %>%
  cbind(rep(c("Mean", "SD"), each = 35)) %>%
  select(., 1:3) %>%
  rename("Stat" = 3, "Values" = 1) %>%
  pivot_wider(names_from = Stat, names_prefix = c("Abun_"), values_from = Values)
```

## Taxonomic

```{r}
pred.epus.tric <- posterior_epred(model.ge.tric.re.sc, newdata = yeardata, re_formula = NA) %>%
  as.tibble() %>%
  summarise_all(.funs = list(mean = mean, sd = sd)) %>%
  t() %>%
  cbind(yeardata) %>%
  cbind(rep(c("Mean", "SD"), each = 35)) %>%
  select(., 1:3) %>%
  rename("Stat" = 3, "Values" = 1) %>%
  pivot_wider(names_from = Stat, names_prefix = c("TRic_"), values_from = Values)
pred.epus.tdiv <- posterior_epred(model.ge.tdiv.re.sc, newdata = yeardata, re_formula = NA) %>%
  as.tibble() %>%
  summarise_all(.funs = list(mean = mean, sd = sd)) %>%
  t() %>%
  cbind(yeardata) %>%
  cbind(rep(c("Mean", "SD"), each = 35)) %>%
  select(., 1:3) %>%
  rename("Stat" = 3, "Values" = 1) %>%
  pivot_wider(names_from = Stat, names_prefix = c("TDiv_"), values_from = Values)
```

## Phylogenetic

```{r}
pred.epus.pric <- posterior_epred(model.ge.pric.re.sc, newdata = yeardata, re_formula = NA) %>%
  as.tibble() %>%
  summarise_all(.funs = list(mean = mean, sd = sd)) %>%
  t() %>%
  cbind(yeardata) %>%
  cbind(rep(c("Mean", "SD"), each = 35)) %>%
  select(., 1:3) %>%
  rename("Stat" = 3, "Values" = 1) %>%
  pivot_wider(names_from = Stat, names_prefix = c("PRic_"), values_from = Values)
pred.epus.pdiv <- posterior_epred(model.ge.pdiv.re.sc, newdata = yeardata, re_formula = NA) %>%
  as.tibble() %>%
  summarise_all(.funs = list(mean = mean, sd = sd)) %>%
  t() %>%
  cbind(yeardata) %>%
  cbind(rep(c("Mean", "SD"), each = 35)) %>%
  select(., 1:3) %>%
  rename("Stat" = 3, "Values" = 1) %>%
  pivot_wider(names_from = Stat, names_prefix = c("PDiv_"), values_from = Values)
```

## Functional

```{r}
pred.epus.fric <- posterior_epred(model.ge.fric.re.sc, newdata = yeardata, re_formula = NA) %>%
  as.tibble() %>%
  summarise_all(.funs = list(mean = mean, sd = sd)) %>%
  t() %>%
  cbind(yeardata) %>%
  cbind(rep(c("Mean", "SD"), each = 35)) %>%
  select(., 1:3) %>%
  rename("Stat" = 3, "Values" = 1) %>%
  pivot_wider(names_from = Stat, names_prefix = c("FRic_"), values_from = Values)
pred.epus.fdiv <- posterior_epred(model.ge.fdiv.re.sc, newdata = yeardata, re_formula = NA) %>%
  as.tibble() %>%
  summarise_all(.funs = list(mean = mean, sd = sd)) %>%
  t() %>%
  cbind(yeardata) %>%
  cbind(rep(c("Mean", "SD"), each = 35)) %>%
  select(., 1:3) %>%
  rename("Stat" = 3, "Values" = 1) %>%
  pivot_wider(names_from = Stat, names_prefix = c("FDiv_"), values_from = Values)
```

## Write results

```{r}
epred.ge <- cbind(pred.ep.abun, pred.ep.tric[,c(2:3)], pred.ep.tdiv[,c(2:3)], 
                  pred.ep.pric[,c(2:3)], pred.ep.pdiv[,c(2:3)], pred.ep.fric[,c(2:3)], pred.ep.fdiv[,c(2:3)])

#write.csv(epred.ge, file = "../outputs/epreds.csv")

epred.ge.us <- cbind(pred.epus.abun, pred.epus.tric[,c(2:3)], pred.epus.tdiv[,c(2:3)], 
                  pred.epus.pric[,c(2:3)], pred.epus.pdiv[,c(2:3)], pred.epus.fric[,c(2:3)], pred.epus.fdiv[,c(2:3)])

#write.csv(epred.ge.us, file = "../outputs/epreds.unscaled.csv")
```

# Set theme

```{r}
theme_base <- theme_set(theme_bw(base_size = 10) + theme(legend.position="bottom")) #create theme
```

# Model plots

## Fig 1

### Legend

```{r}
legend.data <- cbind(c("Coral Cover", "Non-abundance-weighted Richness", "Abundance-weighted Diversity"), seq(1,3,1)) %>%
  as_tibble() %>%
  rename(Metrics = V1, Values = V2)
legend.data$Metrics <- factor(legend.data$Metrics, levels = c("Coral Cover", "Non-abundance-weighted Richness", "Abundance-weighted Diversity"))
plot.legendgraph <- ggplot(data = legend.data) + 
  geom_bar(aes(x = Values, fill = Metrics)) + 
  scale_fill_manual(values = c("Coral Cover" =  "#e31a1c", 
                                 "Non-abundance-weighted Richness" = "#33a02c", 
                                 "Abundance-weighted Diversity" = "#1f78b4"))
plot.legend <- get_legend(plot.legendgraph, position = "left") 
plot.legend <- as_ggplot(plot.legend)
```

### Abundance

```{r}
plot.ge.abun <- plot(conditional_effects(model.ge.abun.re.sc, ask = F), point_args = c(alpha = 0.5, size = 1.5), 
                     points = T, ask=F, line_args = list(colour="#e31a1c", fill="#e31a1c", alpha=0.3))
plot.ge.abun <- plot.ge.abun$Year + labs(x = NULL, y = "Coral Cover")
```

### TRic

```{r}
plot.ge.tric <- plot(conditional_effects(model.ge.tric.re.sc), 
                     point_args = c(alpha = 0.5, size = 1.5), 
                     points = T, ask=F, line_args = list(colour="#33a02c", fill="#33a02c", alpha=0.3))
plot.ge.tric <- plot.ge.tric$Year + labs(x = NULL, y = "Taxonomic Richness")
```

### TDiv

```{r}
plot.ge.tdiv <- plot(conditional_effects(model.ge.tdiv.re.sc), 
                     point_args = c(alpha = 0.5, size = 1.5), 
                     points = T, ask=F, line_args = list(colour="#1f78b4", fill="#1f78b4", alpha=0.3))
plot.ge.tdiv <- plot.ge.tdiv$Year + labs(x = NULL, y = "Taxonomic Diversity")
```

### PRic

```{r}
plot.ge.pric <- plot(conditional_effects(model.ge.pric.re.sc), 
                     point_args = c(alpha = 0.5, size = 1.5), 
                     points = T, ask=F, line_args = list(colour="#33a02c", fill="#33a02c", alpha=0.3))
plot.ge.pric <- plot.ge.pric$Year + labs(x = NULL, y ="Phylogenetic Richness")
```

### PDiv

```{r}
plot.ge.pdiv <- plot(conditional_effects(model.ge.pdiv.re.sc), 
                     point_args = c(alpha = 0.5, size = 1.5), 
                     points = T, ask=F, line_args = list(colour="#1f78b4", fill="#1f78b4", alpha=0.3))
plot.ge.pdiv <- plot.ge.pdiv$Year + labs(x = NULL, y ="Phylogenetic Diversity")
```

### FRic

```{r}
plot.ge.fric <- plot(conditional_effects(model.ge.fric.re.sc), 
                     point_args = c(alpha = 0.5, size = 1.5), 
                     points = T, ask=F, line_args = list(colour="#33a02c", fill="#33a02c", alpha=0.3))
plot.ge.fric <- plot.ge.fric$Year + labs(x = NULL, y ="Functional Richness")
```

### FDiv

```{r}
plot.ge.fdiv <- plot(conditional_effects(model.ge.fdiv.re.sc), 
                     point_args = c(alpha = 0.5, size = 1.5), 
                     points = T, ask=F, line_args = list(colour="#1f78b4", fill="#1f78b4", alpha=0.3))
plot.ge.fdiv <- plot.ge.fdiv$Year + labs(x = NULL, y ="Functional Diversity")
```

### Combined Plot

```{r}
layout.model <- "
#A
BC
DE
FG"

plot.gescmodel <- plot.legend + plot.ge.abun + plot.ge.tric + plot.ge.tdiv +  
  plot.ge.pric +  plot.ge.pdiv + plot.ge.fric + plot.ge.fdiv + 
  plot_layout(ncol = 2) + plot_annotation(tag_levels = list(c("", "a", "b", "c", "d", "e", "f", "g")))

#ggsave(plot.gescmodel, file = "../outputs/figs/modeleffects.ge.sc.tiff", dpi=300, width=10, height=10)
#ggsave(plot.gescmodel, file = "../outputs/figs/modeleffects.ge.sc.pdf", width=10, height=10)
```

## Fig 2

### Genus richness correlations

```{r}
plot.cor.prs <- plot(conditional_effects(cor.pric.sc2), point_args = c(alpha = 0.5, size = 1.5), 
                     points = T, ask=F, line_args = list(colour="#33a02c", fill="#33a02c", alpha=0.3))
plot.cor.prs <- plot.cor.prs$TRic + labs(x = "Taxonomic Richness", y ="Phylogenetic Richness")
plot.cor.frs <- plot(conditional_effects(cor.fric.sc2), point_args = c(alpha = 0.5, size = 1.5), 
                     points = T, ask=F, line_args = list(colour="#33a02c", fill="#33a02c", alpha=0.3))
plot.cor.frs <- plot.cor.frs$TRic + labs(x = "Taxonomic Richness", y ="Functional Richness")
plot.cor.pfrs <- plot(conditional_effects(cor.pfric.sc2), point_args = c(alpha = 0.5, size = 1.5), 
                     points = T, ask=F, line_args = list(colour="#33a02c", fill="#33a02c", alpha=0.3))
plot.cor.pfrs <- plot.cor.pfrs$PRic + labs(x = "Phylogenetic Richness", y ="Functional Richness")
```

### Genus diversity correlations

```{r}
plot.cor.pds <- plot(conditional_effects(cor.pdiv.sc2), point_args = c(alpha = 0.5, size = 1.5), 
                     points = T, ask=F, line_args = list(colour="#1f78b4", fill="#1f78b4", alpha=0.3))
plot.cor.pds <- plot.cor.pds$TDiv + labs(x = "Taxonomic Diversity", y ="Phylogenetic Diversity")
plot.cor.fds <- plot(conditional_effects(cor.fdiv.sc2), point_args = c(alpha = 0.5, size = 1.5), 
                     points = T, ask=F, line_args = list(colour="#1f78b4", fill="#1f78b4", alpha=0.3))
plot.cor.fds <- plot.cor.fds$TDiv + labs(x = "Taxonomic Diversity", y ="Functional Diversity")
plot.cor.pfds <- plot(conditional_effects(cor.pfdiv.sc2), point_args = c(alpha = 0.5, size = 1.5), 
                      points = T, ask=F, line_args = list(colour="#1f78b4", fill="#1f78b4", alpha=0.3))
plot.cor.pfds <- plot.cor.pfds$PDiv + labs(x = "Phylogenetic Diversity", y ="Functional Diversity")
```

### Species richness correlations

```{r}
plot.scor.prs <- plot(conditional_effects(scor.pric.sc2), point_args = c(alpha = 0.5, size = 1.5), 
                     points = T, ask=F, line_args = list(colour="#33a02c", fill="#33a02c", alpha=0.3))
plot.scor.prs <- plot.scor.prs$TRic + labs(x = "Taxonomic Richness", y ="Phylogenetic Richness")
plot.scor.frs <- plot(conditional_effects(scor.fric.sc2), point_args = c(alpha = 0.5, size = 1.5), 
                     points = T, ask=F, line_args = list(colour="#33a02c", fill="#33a02c", alpha=0.3))
plot.scor.frs <- plot.scor.frs$TRic + labs(x = "Taxonomic Richness", y ="Functional Richness")
plot.scor.pfrs <- plot(conditional_effects(scor.pfric.sc2), point_args = c(alpha = 0.5, size = 1.5), 
                      points = T, ask=F, line_args = list(colour="#33a02c", fill="#33a02c", alpha=0.3))
plot.scor.pfrs <- plot.scor.pfrs$PRic + labs(x = "Phylogenetic Richness", y ="Functional Richness")
```

### Species diversity correlations

```{r}
plot.scor.pds <- plot(conditional_effects(scor.pdiv.sc2), point_args = c(alpha = 0.5, size = 1.5), 
                     points = T, ask=F, line_args = list(colour="#1f78b4", fill="#1f78b4", alpha=0.3))
plot.scor.pds <- plot.scor.pds$TDiv + labs(x = "Taxonomic Diversity", y ="Phylogenetic Diversity")
plot.scor.fds <- plot(conditional_effects(scor.fdiv.sc2), point_args = c(alpha = 0.5, size = 1.5), 
                     points = T, ask=F, line_args = list(colour="#1f78b4", fill="#1f78b4", alpha=0.3))
plot.scor.fds <- plot.scor.fds$TDiv + labs(x = "Taxonomic Diversity", y ="Functional Diversity")
plot.scor.pfds <- plot(conditional_effects(scor.pfdiv.sc2), point_args = c(alpha = 0.5, size = 1.5), 
                      points = T, ask=F, line_args = list(colour="#1f78b4", fill="#1f78b4", alpha=0.3))
plot.scor.pfds <- plot.scor.pfds$PDiv + labs(x = "Phylogenetic Diversity", y ="Functional Diversity")
```

### Combined plot

```{r}
layout.cor <- "
ABC
DEF
GHI
JKL"

plot.cor <- plot.cor.prs + plot.cor.frs + plot.cor.pfrs +  
  plot.cor.pds +  plot.cor.fds + plot.cor.pfds + 
  plot.scor.prs + plot.scor.frs + plot.scor.pfrs +
  plot.scor.pds + plot.scor.fds + plot.scor.pfds + 
  plot_layout(design = layout.cor) + plot_annotation(tag_levels = 'a')

#ggsave(plot.cor, file = "../outputs/figs/model.cor.tiff", dpi=300, width=10, height=12)
#ggsave(plot.cor, file = "../outputs/figs/model.cor.pdf", width=10, height=12)
```

## Fig 3

### Abundance

```{r}
plot.sp.abun <- plot(conditional_effects(model.sp.abun.re.sc, ask = F), point_args = c(alpha = 0.5, size = 1.5), 
                     points = T, ask=F, cat_args = list(colour="#e31a1c", alpha=0.7), 
                     errorbar_args = list(colour="#e31a1c", size=1.25, alpha = 0.7))
plot.sp.abun <- plot.sp.abun$Period + labs(x = NULL, y = "Coral Cover")
```

### TRic

```{r}
plot.sp.tric <- plot(conditional_effects(model.sp.tric.re.sc, ask = F), 
                     point_args = c(alpha = 0.5, size = 1.5), 
                     points = T, ask=F, cat_args = list(colour="#33a02c", alpha=0.7), 
                     errorbar_args = list(colour="#33a02c", size=1.25, alpha = 0.7))
plot.sp.tric <- plot.sp.tric$Period + labs(x = NULL, y = "Taxonomic Richness")
```

### TDiv

```{r}
plot.sp.tdiv <- plot(conditional_effects(model.sp.tdiv.re.sc), 
                     point_args = c(alpha = 0.5, size = 1.5), 
                     points = T, ask=F, cat_args = list(colour="#1f78b4", alpha=0.7), 
                     errorbar_args = list(colour="#1f78b4", size=1.25, alpha = 0.7))
plot.sp.tdiv <- plot.sp.tdiv$Period + labs(x = NULL, y = "Taxonomic Diversity")
```

### PRic

```{r}
plot.sp.pric <- plot(conditional_effects(model.sp.pric.re.sc), 
                     point_args = c(alpha = 0.5, size = 1.5), 
                     points = T, ask=F, cat_args = list(colour="#33a02c", alpha=0.7), 
                     errorbar_args = list(colour="#33a02c", size=1.25, alpha = 0.7))
plot.sp.pric <- plot.sp.pric$Period + labs(x = NULL, y ="Phylogenetic Richness")
```

### PDiv

```{r}
plot.sp.pdiv <- plot(conditional_effects(model.sp.pdiv.re.sc), 
                     point_args = c(alpha = 0.5, size = 1.5), 
                     points = T, ask=F, cat_args = list(colour="#1f78b4", alpha=0.7), 
                     errorbar_args = list(colour="#1f78b4", size=1.25, alpha = 0.7))
plot.sp.pdiv <- plot.sp.pdiv$Period + labs(x = NULL, y ="Phylogenetic Diversity")
```

### FRic

```{r}
lot.sp.fric <- plot(conditional_effects(model.sp.fric.re.sc), 
                     point_args = c(alpha = 0.5, size = 1.5), 
                     points = T, ask=F, cat_args = list(colour="#33a02c", alpha=0.7), 
                     errorbar_args = list(colour="#33a02c", size=1.25, alpha = 0.7))
plot.sp.fric <- plot.sp.fric$Period + labs(x = NULL, y ="Functional Richness")
```

### FDiv

```{r}
plot.sp.fdiv <- plot(conditional_effects(model.sp.fdiv.re.sc), 
                     point_args = c(alpha = 0.5, size = 1.5), 
                     points = T, ask=F, cat_args = list(colour="#1f78b4", alpha=0.7), 
                     errorbar_args = list(colour="#1f78b4", size=1.25, alpha = 0.7))
plot.sp.fdiv <- plot.sp.fdiv$Period + labs(x = NULL, y ="Functional Diversity")
```

### Combined plot

```{r}
#plot.spscmodel <- plot.sp.abun + plot.sp.tric + plot.sp.tdiv +  
#  plot.sp.pric +  plot.sp.pdiv + plot.sp.fric + plot.sp.fdiv + 
#  plot_layout(design = layout.model) + plot_annotation(tag_levels = 'a')

#ggsave(plot.spscmodel, file = "../outputs/figs/modeleffects.sp.sc.tiff", dpi=300, width=10, height=10)
#ggsave(plot.spscmodel, file = "../outputs/figs/modeleffects.sp.sc.pdf", width=10, height=10)

plot.spscmodel2 <- plot.sp.tric + plot.sp.tdiv +  
  plot.sp.pric +  plot.sp.pdiv + plot.sp.fric + plot.sp.fdiv + 
  plot_layout(ncol = 2) + plot_annotation(tag_levels = 'a')

#ggsave(plot.spscmodel2, file = "../outputs/figs/modeleffects.sp.sc2.tiff", dpi=300, width=10, height=10)
#ggsave(plot.spscmodel2, file = "../outputs/figs/modeleffects.sp.sc2.pdf", width=10, height=10)
```

## Fig 4

### Continuous traits

```{r}
plot.ge.grow <- plot(conditional_effects(model.ge.grow.re.sc), 
                     point_args = c(alpha = 0.5, size = 1.5), 
                     points = T, ask=F, line_args = list(colour="#1f78b4", fill="#1f78b4", alpha=0.3))
plot.ge.grow <- plot.ge.grow$Year + labs(x = NULL, y = "Growth Rate*")
plot.ge.grow <- plot.ge.grow + ylim(-2.5,4) 
plot.ge.skel <- plot(conditional_effects(model.ge.skel.re.sc), 
                     point_args = c(alpha = 0.5, size = 1.5), 
                     points = T, ask=F, line_args = list(colour="#1f78b4", fill="#1f78b4", alpha=0.3))
plot.ge.skel <- plot.ge.skel$Year + labs(x = NULL, y = "Skeletal Density*")
plot.ge.skel <- plot.ge.skel + ylim(-3,4) 
plot.ge.cwid <- plot(conditional_effects(model.ge.cwid.re.sc), 
                     point_args = c(alpha = 0.5, size = 1.5), 
                     points = T, ask=F, line_args = list(colour="#1f78b4", fill="#1f78b4", alpha=0.3))
plot.ge.cwid <- plot.ge.cwid$Year + labs(x = NULL, y ="Corallite Width*")
plot.ge.cwid <- plot.ge.cwid + ylim(-1,4) 
plot.ge.cmd <- plot(conditional_effects(model.ge.cmd.re.sc), 
                     point_args = c(alpha = 0.5, size = 1.5), 
                     points = T, ask=F, line_args = list(colour="#1f78b4", fill="#1f78b4", alpha=0.3))
plot.ge.cmd <- plot.ge.cmd$Year + labs(x = NULL, y ="Colony Max Diameter*")
plot.ge.cmd <- plot.ge.cmd + ylim(-2.5,4) 
```

### Growth forms

```{r}
plot.ge.gfbr <- plot(conditional_effects(model.ge.gfbr.re.sc), 
                     point_args = c(alpha = 0.5, size = 1.5), 
                     points = T, ask=F, line_args = list(colour="#1f78b4", fill="#1f78b4", alpha=0.3))
plot.ge.gfbr <- plot.ge.gfbr$Year + labs(x = NULL, y = "Branching Morphology*")
plot.ge.gfbr <- plot.ge.gfbr + ylim(-1, 4)
plot.ge.gfen <- plot(conditional_effects(model.ge.gfen.re.sc), 
                     point_args = c(alpha = 0.5, size = 1.5), 
                     points = T, ask=F, line_args = list(colour="#1f78b4", fill="#1f78b4", alpha=0.3))
plot.ge.gfen <- plot.ge.gfen$Year + labs(x = NULL, y = "Encrusting Morphology")
plot.ge.gfla <- plot(conditional_effects(model.ge.gfla.re.sc), 
                     point_args = c(alpha = 0.5, size = 1.5), 
                     points = T, ask=F, line_args = list(colour="#1f78b4", fill="#1f78b4", alpha=0.3))
plot.ge.gfla <- plot.ge.gfla$Year + labs(x = NULL, y = "Laminar Morphology")
plot.ge.gfma <- plot(conditional_effects(model.ge.gfma.re.sc), 
                     point_args = c(alpha = 0.5, size = 1.5), 
                     points = T, ask=F, line_args = list(colour="#1f78b4", fill="#1f78b4", alpha=0.3))
plot.ge.gfma <- plot.ge.gfma$Year + labs(x = NULL, y = "Massive Morphology")
plot.ge.gfsu <- plot(conditional_effects(model.ge.gfsu.re.sc), 
                     point_args = c(alpha = 0.5, size = 1.5), 
                     points = T, ask=F, line_args = list(colour="#1f78b4", fill="#1f78b4", alpha=0.3))
plot.ge.gfsu <- plot.ge.gfsu$Year + labs(x = NULL, y = "Submassive Morphology")
```

### Combined plot

```{r}
plot.ge.cwm <- plot.ge.grow + plot.ge.skel + plot.ge.cwid + plot.ge.cmd +
  plot_layout(ncol = 1) + plot_annotation(tag_levels = 'a')

plot.ge.gf <- plot.ge.gfbr + plot.ge.gfen + plot.ge.gfla + plot.ge.gfsu + plot.ge.gfma +
  plot_layout(ncol = 1) + plot_annotation(tag_levels = list(c("e", "f", "g", "h", "i")))

plot.ge.cwmgf <- (plot.ge.cwm | plot.ge.gf)  + plot_annotation(tag_levels = 'a')

#ggsave(plot.ge.cwmgf, file = "../outputs/figs/modeleffects.ge.cwmgf.tiff", dpi=300, width=10, height=12)
#ggsave(plot.ge.cwmgf, file = "../outputs/figs/modeleffects.ge.cwmgf.pdf", width=10, height=12)
```

## Supplementary pltos

### Genus ranef

```{r}
abun.ranef <- plot_coefficients(model.ge.abun.re.sc, ranef = TRUE, which_ranef = 'Site') + coord_flip()
tric.ranef <- plot_coefficients(model.ge.tric.re.sc, ranef = TRUE, which_ranef = 'Site') + coord_flip()
tdiv.ranef <- plot_coefficients(model.ge.tdiv.re.sc, ranef = TRUE, which_ranef = 'Site') + coord_flip()
pric.ranef <- plot_coefficients(model.ge.pric.re.sc, ranef = TRUE, which_ranef = 'Site') + coord_flip()
pdiv.ranef <- plot_coefficients(model.ge.pdiv.re.sc, ranef = TRUE, which_ranef = 'Site') + coord_flip()
fric.ranef <- plot_coefficients(model.ge.fric.re.sc, ranef = TRUE, which_ranef = 'Site') + coord_flip()
fdiv.ranef <- plot_coefficients(model.ge.fdiv.re.sc, ranef = TRUE, which_ranef = 'Site') + coord_flip()

plot.ge.ranef <- abun.ranef + tric.ranef + tdiv.ranef + 
  pric.ranef + pdiv.ranef + fric.ranef + fdiv.ranef + 
  plot_layout(design = layout.model) + 
  plot_annotation(tag_levels = list(c("a) Cover", "b) TRic", "c) TDiv", "d) PRic", "e) PDiv", "f) FRic", "f) FDiv")))

#ggsave(plot.ge.ranef, file = "../outputs/figs/modelraneffects.ge.tiff", dpi=300, width=10, height=15)
#ggsave(plot.ge.ranef, file = "../outputs/figs/modelraneffects.ge.pdf", width=10, height=15)
```

### Species ranef

```{r}
abuns.ranef <- plot_coefficients(model.sp.abun.re.sc, ranef = TRUE, which_ranef = 'Site') + coord_flip()
trics.ranef <- plot_coefficients(model.sp.tric.re.sc, ranef = TRUE, which_ranef = 'Site') + coord_flip()
tdivs.ranef <- plot_coefficients(model.sp.tdiv.re.sc, ranef = TRUE, which_ranef = 'Site') + coord_flip()
prics.ranef <- plot_coefficients(model.sp.pric.re.sc, ranef = TRUE, which_ranef = 'Site') + coord_flip()
pdivs.ranef <- plot_coefficients(model.sp.pdiv.re.sc, ranef = TRUE, which_ranef = 'Site') + coord_flip()
frics.ranef <- plot_coefficients(model.sp.fric.re.sc, ranef = TRUE, which_ranef = 'Site') + coord_flip()
fdivs.ranef <- plot_coefficients(model.sp.fdiv.re.sc, ranef = TRUE, which_ranef = 'Site') + coord_flip()

plot.sp.ranef <- abuns.ranef + trics.ranef + tdivs.ranef + 
  prics.ranef + pdivs.ranef + frics.ranef + fdivs.ranef + 
  plot_layout(design = layout.model) + 
  plot_annotation(tag_levels = list(c("a) Cover", "b) TRic", "c) TDiv", "d) PRic", "e) PDiv", "f) FRic", "f) FDiv")))

#ggsave(plot.sp.ranef, file = "../outputs/figs/modelraneffects.sp.tiff", dpi=300, width=10, height=12)
#ggsave(plot.sp.ranef, file = "../outputs/figs/modelraneffects.sp.pdf", width=10, height=12)
```
